---
title: "Understanding College Students Concerns during COVID-19 in Michigan"
author: "Jacy Li;Chendi Zhao"
date: "2020/12/6"
output:
  word_document: default
  html_document: default
---

#set up
```{r include=F}
if(!require(stm)) install.packages("stm")
if(!require(quanteda)) install.packages("quanteda")
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(lubridate)) install.packages("lubridate")
if(!require(RTextTools)) install.packages("RTextTools")
if(!require(igraph)) install.packages("igraph")
if(!require(wordcloud)) install.packages("wordcloud")
library(stm)
library(quanteda)
library(lubridate)
library(RTextTools)
library(igraph)
library(wordcloud)
library(ggplot2)
```
#load files
```{r include=FALSE,message=FALSE}
#setwd("C:/Users/赵晨笛/Desktop/DATA 727/all data")
setwd("C:/Users/jacyli/Box/727")
data<-read.csv("pooleddata.csv")

```

#prepare: associate text with metadata
#The Structural Topic Model allows researchers to flexibly estimate a topic model that includes document-level metadata. Estimation is accomplished through a fast variational approximation.
```{r results='hide'}
#creates a document term matrix that can be supplied directly to the stm model fitting function.
processed <- textProcessor(data$selftext, metadata = data)

#stemming (reducing words to their root form), dropping punctuation and stop word removal (e.g., the, is, at)
#prepDocuments also removes infrequent terms depending on the user-set parameter lower.thresh.
out <- prepDocuments(processed$documents,
                     processed$vocab,
                     processed$meta, 
                     lower.thresh = 15)
docs <- out$documents
vocab <- out$vocab
meta <-out$meta

```

# Estimate the STM 
```{r results='hide'}
redditFit <- stm(documents = out$documents, 
                       vocab =out$vocab,
                       K = 20,
                       prevalence =~ratio+s(created_utc),
                       max.em.its = 50, data = out$meta,
                       init.type = "Spectral")

```

```{r}
labelTopics(redditFit, 1:20)

```

#Estimating metadata and topic relationships
```{r results='hide'}
prep_prev <- estimateEffect(1:20 ~ratio+s(created_utc), 
                       redditFit,
                       meta = out$meta, 
                       uncertainty = "Global")

```

#Visualizaton: Presenting STM results

#1.estimated topic proportions
```{r}
plot(redditFit, type = "summary", xlim = c(0,0.3))

```

#2. Graphical display of topic prevalence
```{r fig.height =5, fig.width = 10}
plot(prep_prev, 
     "created_utc", 
      method = "continuous", 
      topics =c(2,3,4,5,11),
     ci.level=F,
      printlegend = TRUE,
      xaxt = "n", 
      xlab = "time",
      ylim = c(0,0.15))

plot(prep_prev, 
     "created_utc", 
      method = "continuous", 
      topics =c(9,12,13),
      ci.level=F,
      printlegend = TRUE,
      xaxt = "n", 
      xlab = "time")
```
# Estimate the STM with content 
```{r results='hide'}
redditFit_c <- stm(documents = out$documents, 
                       vocab =out$vocab,
                       K = 20,
                       prevalence =~ratio+s(created_utc),
                       content = ~mode,
                       max.em.its = 50, data = out$meta,
                       init.type = "Spectral")

```

```{r}
labelTopics(redditFit_c, 1:20)

```
