---
title: "Fundamentals of Computing and Data Display"
subtitle: "Term paper"
author: "Jacy Li and Chendi Zhao"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    df_print: kable
references:
- id: Murphy2005
  title: A meto-analysis of hypothetical bias in stated preference valuation
  author:
  - family: Murphy
    given: James
  - family: Allen
    given: P.
  - family: Stevens
    given: Thomas
  - family: Weatherhead
    given: Darryl
  container-title: Environmental and Resource Economics
  volume: 30
  issue: 3
  page: 313-325
  type: article-journal
  issued:
    year: 2005
- id: 
  title: 
  author: 
  - family: 
    given: 
  - family: 
    given: 
  - family: 
    given: 
  type: 
  publisher: 
  issued: 
    year: 
---

```{r, include = FALSE}
library(knitr)
library(tidyverse)
```

## Introduction

This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].

Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e. the text sections are more detailed and big or redundant code chunks can be hidden.

### Draft
The COVID-19 pandemic has spread worldwide, impacting every aspect of daily life. In an emergency event of such kind that persists, it becomes increasingly important to have reliable, up-to-date emergency management assessments. The ability to accurately capture public needs and attitudes are critical to the success of emergency response plans. 

The traditional methods, such as surveys, have several pitfalls to understanding these issues. Most surveys introduce hypothetical bias as subjects' responses are measured under hypothetical scenarios [@Murphy]. Besides, as response rates fall, costs rise, and the desire for timely data increases, social media are becoming increasingly popular as a source of data for social science research. Reddit, the self-proclaimed "front page of the Internet" with its unique feature of subreddits, opens up potentials to study smaller geographies and rarer subpopulations.

This study focuses on college students' responses to COVID-19 emergency management and the variability across time and groups in Michigan. Using Reddit data, we collect organic submissions in text formats from corresponding subreddits of the ten largest colleges and universities in Michigan for the period of March 1st, 2020, to October 31st, 2020. Taking a topic modeling approach, we derive COVID-19 related topics of our interest. We further divide reference time by academic schedule (Spring Semester, Summer Vacation, and Fall Semester) and implement a dynamic topic model to capture the information changing over time and variability among universities. We present the student group's social media landscape and shed light on the implications of different locations and school emergency management plans on student responses. 

## Data

This section describes the data sources and the data gathering process.

```{r}
# A code chunk that exemplifies the data gathering process
```

```{r, include = FALSE}
# Additional code chunks that repeat tasks or do basic things can be hidden
```

## Results

This section presents the main results.

### Data exploration

The results section may have a data exploration part, but in general the structure here depends on the specific project.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

### Analysis

This section presents the main results, such as (for example) stats and graphs that show relationships, model results and/or clustering, PCA, etc.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

## Discussion

This section summarizes the results and may briefly outline advantages and limitations of the work presented.

## References
